---
title: "R Project 1"
author: "Thanh La"
date: "9/11/2020"
output: html_document
---


### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

```{r include  = FALSE}
a = datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```
There are 13 rows and 2 columns.

There are 2 variables name "dataset" and "n".


### Exercise 2

Plot coordinate for the dinosaur dataset:

```{r plot-dino, fig.height=3, fig.width=6,}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) + geom_point()
```

Calculate the correlation between `x` and `y` in Dinosaur dataset:
```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plot coordinate for the star dataset:
```{r plot-star, fig.height=3, fig.width= 5}
star_data = datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()


```

Calculate the correlation between `x` and `y` in Star dataset:
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

Plot coordinate for the circle dataset:

```{r plot_circle, fig.height=2, fig.width=4}
circle_data = datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x=x, y=y)) + geom_point()


```

Calculate the correlation between `x` and `y` in Circle dataset:
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))


```

### Exercise 5

```{r}
ggplot(datasaurus_dozen, aes(x=x, y=y, color = dataset)) + 
  geom_point() + 
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)

```
